Domain Tree Analysis

### 2017-08-24 domain_level/TextS4_domain_tree_analysis.Rmd
nearly done new domain graph

```{r}
norm_counts <- counts(dds, normalized=TRUE)
sigUp_norm_counts <- norm_counts[rownames(norm_counts) %in% rownames(resUp),]

percent_counts <- t(t(sigUp_norm_counts)/colSums(norm_dom_counts))

sigUp_norm_counts_df <- melt(percent_counts)
colnames(sigUp_norm_counts_df) <- c("Domain Cluster", "Isolate", "Proportion of expression")
sigUp_norm_counts_df$disease[grepl("^S.*",sigUp_norm_counts_df$Isolate)]<-"severe"
sigUp_norm_counts_df$disease[!grepl("^S.*",sigUp_norm_counts_df$Isolate)]<-"non-severe"
colnames(sigUp_norm_counts_df) <- c("Domain Cluster", "Isolate", "Proportion of VAR expression", "Phenotype")

gg <- ggplot(sigUp_norm_counts_df, aes(x=Phenotype, y=`Proportion of VAR expression`
                                       , colour=Phenotype))
gg <- gg + geom_boxplot(outlier.shape = NA) + geom_jitter(width = 0.2, height = 0)
gg <- gg + facet_wrap(~`Domain Cluster`, scales = "free_y") + theme_bw()
gg <- gg + scale_colour_manual(values = colors)
gg
```

>>>>

```{r}
rpkm_dom_clus <- counts(dds, normalized=FALSE)
rpkm_dom_clus <- rpkm_dom_clus[rownames(rpkm_dom_clus) %in% rownames(resUp),]
dom_length_vector <- domain_length_matrix[cluster_domain_type[rownames(rpkm_dom_clus)],]
rownames(rpkm_dom_clus) <- paste(rownames(rpkm_dom_clus),
                           cluster_domain_type[rownames(rpkm_dom_clus)] ,
                           sep=" - ")
rpkm_dom_clus <- (t(t(rpkm_dom_clus)/domain_lib_size)/dom_length_vector)*10^9

rpkm_dom_clus <- rpkm_dom_clus+1 #to deal with log transformation
sigUp_norm_counts_clus_df <- melt(rpkm_dom_clus)
colnames(sigUp_norm_counts_clus_df) <- c("Domain Cluster", "Isolate", "RPKM")

sigUp_norm_counts_clus_df$disease[grepl("^S.*",sigUp_norm_counts_clus_df$Isolate)]<-"severe"
sigUp_norm_counts_clus_df$disease[!grepl("^S.*",sigUp_norm_counts_clus_df$Isolate)]<-"non-severe"
colnames(sigUp_norm_counts_clus_df) <- c("Domain Cluster", "Isolate", "RPKM", "Phenotype")

gg <- ggplot(sigUp_norm_counts_clus_df, aes(x=Phenotype, y=RPKM
                                       , colour=Phenotype))
gg <- gg + geom_boxplot(outlier.shape = NA) + geom_jitter(width = 0.2, height = 0)
gg <- gg + facet_wrap(~`Domain Cluster`) + theme_bw()
gg <- gg + scale_colour_manual(values = colors) + scale_y_log10()
gg
```
